MLH1 Results Outline

### 2020-02-12 doc/Results.rmd
encountering bugs when knitting

load(file="~./MLH1repo/data/CleanBivData_11.2.20.RData")

@@

```{r Q1.SC.show.long.biv, echo=FALSE}

mouse.shoo.long.biv <- ggplot(real.long.bivData, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Mouse av. \nMale Long Biv SC Lengths")
mouse.shoo.long.biv

```{r Q2.SC.long.biv, echo=FALSE}
male.long.biv <- real.long.bivData %>% filter(sex== "male")

@@

```{r Q2.SC.long.biv, echo=FALSE}
male.long.biv <- real.long.bivData %>% filter(sex== "male")

@@

```{r Q2.SC.long.biv, echo=FALSE}

@@

>>>>

load(file="~./MLH1repo/data/CleanBivData_12.2.20.RData")

@@

```{r Q1.SC.show.long.biv, echo=FALSE, eval=FALSE}

mouse.shoo.long.biv <- ggplot(real.long.bivData, aes(y=chromosomeLength, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Mouse av. \nMale Long Biv SC Lengths")
mouse.shoo.long.biv

```{r Q2.SC.long.biv_wacko, echo=FALSE}
male.long.biv <- real.long.bivData %>% filter(sex== "male")

@@

```{r Q2.SC.long.biv_2, echo=FALSE}
male.long.biv <- real.long.bivData %>% filter(sex== "male")

@@

```{r Q2.SC.long.biv_3, echo=FALSE}

@@

#mouse.av.long.biv.table <- make this is set up
